Fig2: Candidate genes

### 2020-05-03 analysis/figure-2.Rmd
now with music notes

```{r setup, message=F}
library(tidyverse)
library(ggtext)
library(cowplot)
library(ggpubr)
library(knitr)
library(kableExtra)
library(corrr)
library(ggsignif)

@@

plot_grid(a,b,c,d,e,f,g,h,i,j,k,l, nrow = 3, 
          rel_widths = c(0.8,0.8,1,1), rel_heights = c(1,1,1.2),
          labels = c("A", " ", "B", "",
                     "C", " ", "D", "",
                     "E", " ", "F", ""), label_size =  8)

>>>>

```{r setup, message=F}
library(tidyverse)
library(ggtext)
library(cowplot)
library(ggpubr)
library(knitr)
library(kableExtra)
library(corrr)
library(ggsignif)
library(magick)
library(scales)
library(ggimage)

@@

atof <- plot_grid(a,b,c,d,e,f,g,h,i,j,k,l, nrow = 3, 
          rel_widths = c(0.8,0.8,1,1), rel_heights = c(1,1,1.2),
          labels = c("A", " ", "B", "",
                     "C", " ", "D", "",
                     "E", " ", "F", ""), label_size =  8)

musicplot <- function(whichgene, whichtissue){

    treble <- magick::image_read("../figures/images/fig_treble.png")
    base <- magick::image_read("../figures/images/fig_base.png")

    p <- candidatevsd %>%
      group_by(treatment, tissue, gene, sex)  %>% 
      summarize(median = median(counts, na.rm = T), 
                se = sd(counts,  na.rm = T)/sqrt(length(counts))) %>%
      dplyr::mutate(scaled = rescale(median, to = c(0, 7))) %>%
      dplyr::mutate(image = "../figures/images/musicnote.png")   %>%
      filter(
        gene %in% whichgene,
        tissue %in% whichtissue      ) %>% 
      collect() %>%
      drop_na() %>%
      filter(treatment != "control") %>%
      ggplot( aes(x = treatment, y = median)) +
      geom_errorbar(aes(ymin = median - se, 
                        ymax = median + se, color = "white"),  width=0) +
      geom_image(aes(image=image), size = 0.1)+
      theme_void(base_size = 7) +
      theme(legend.position = "none",
            title = element_text(face = "italic"),
            strip.text = element_text(color = "white")) +
      scale_color_manual(values = allcolors) +
      labs(y = " ", subtitle = " " ) +
      facet_wrap(~sex, nrow = 2, scales = "free_y")
      return(p)
}

scales <- png::readPNG("../figures/images/fig_music.png")
scales <- ggdraw() +  draw_image(scales, scale = 1)

p1 <- musicplot(c("DRD1", "HTR2C"), "hypothalamus") + labs(subtitle = " D1DR & HTR2C", title = " " )
p2 <- musicplot(c("AVPR1A", "CRHR1"), "pituitary") + labs(subtitle = " AVPR1A & CRHR1 ", title = " " )
p3 <- musicplot(c("ESR1", "PGR"), "gonad") + labs(subtitle = "  ESR1 & PGR", title = " ")

p123 <- plot_grid(p1, NULL,  p2, NULL,p3, NULL,ncol = 1, rel_heights = c(1,0.2,1,0.2,1.2,0.2))

plot_grid(atof, scales, p123, rel_widths = c(1.5,0.1, 0.3), ncol = 3)
```
